---
title: "Assignment 0"
author: "Mohammadkhashayar Alavi"
date: '2019-02-15'
output:
  pdf_document: default
  html_document: default
---

In this assignment we learn how to write simple scripts with R to do simple tasks.

The document containing instructions and Todos can be downloaded from [here](https://cran.r-project.org/doc/contrib/Torfs+Brauer-Short-R-Intro.pdf).

Github has been used to store each step of the process. A commit has been pushed to my repository after each Todo. The username used for github: **malavi3**

My repository can be reached [here](https://github.com/malavi3/srtgit)

The code and output for each Todo is mentioned below.

####Todo 1
```{r}
((2017-2014)/(2014-1993))*100
```

####Todo 2
```{r}
a = 2014
b = 2017
c = 1993
((b-a)/(a-c))*100
```

####Todo 3
```{r}
a=c(4,5,8,11)
sum(a)
```

####Todo 4
```{r}
x=rnorm(100)
plot(x)
```

####Todo 5
```{r}
help(sqrt)
```

####Todo 6
```{r}
source("~/srtgit/firstscript.R")
```

####Todo 7
```{r}
P = seq(from=31, to=60, by=1)
Q = matrix(data=P,ncol=5,nrow=6)
Q 
```

####Todo 8
```{r}
x1=c(rnorm(100))
x2=c(rnorm(100))
x3=c(rnorm(100))
t=data.frame(a=c(x1), b=c(x1+x2), c=c(x1+x2+x3))
plot(t)
```

####Todo 9
```{r}
x1=c(rnorm(100))
x2=c(rnorm(100))
x3=c(rnorm(100))
t=data.frame(a=c(x1), b=c(x1+x2), c=c(x1+x2+x3))
plot(t$a, type="l", ylim=range(t), lwd=3, col=rgb(1,0,0,0.3))
lines(t$b, type="s", lwd=2, col=rgb(0.3,0.4,0.3,0.9))
points(t$c, pch=20, cex=4, col=rgb(0,0,1,0.3))
```

####Todo 10
```{r}
d2 = read.table(file="~/srtgit/tst1.txt", header=TRUE)
d2$g <- d2$g*5
write.table(d2, file="~/srtgit/tst2.txt", row.names=FALSE)
```

####Todo 11

In this Todo I used pmax with sqrt as without it a NANS error would be given.

```{r}
a=rnorm(100)
b=sqrt(pmax(0,a))
mean(b)
```

####Todo 12
```{r}
x=strptime(c("20190217", "20141206", "20190504"), format="%Y%m%d")
y=c(0,0,5)
plot(x,y)
```

####Todo Extra
```{r}
a=1:100
a[1:4] <- a[1:4]*10
a[91:100] <- a[91:100]*10
a[5:90] <- a[5:90]*0.1
a
```


#####Resources

[How to present data in Github](https://www.dataquest.io/blog/how-to-share-data-science-portfolio/)

[How to use rmarkdown with rstudio](http://rmarkdown.rstudio.com/)


